### 2018-02-22 paper/algorithm.tex

\NewCryptoEntity{\Alice}{A}
\NewCryptoEntity{\Bob}{B}
\NewCryptoEntity{\Carol}{C}
\NewCryptoEntity{\David}{D}

We have several participants: Alice, Bob, Carol and David.
Each of them has a set of devices, \(D_i\) (where \(i\in \{\Alice, \Bob, \Carol, 
  \David\}\)).
We have two protocols to track knowledge: one protocol which is run between the 
devices in \(D_i\) (the Device Swarm Protocol) to gain knowledge on the 
swarm, and another run between different swarms (the Inter-Swarm Protocol) to 
keep global knowledge.
Finally, we have a file-sharing protocol which uses the local and global 
knowledges to coordinate file sharing between devices in different swarms.

@@

\subsection{File-sharing protocol}

>>>>

\NewCryptoEntity{\Alfred}{A}
\NewCryptoEntity{\Beth}{B}
\NewCryptoEntity{\Cathy}{C}
\NewCryptoEntity{\David}{D}

We consider several participants: Alfred, Beth, Cathy and David.
Each of them has a set of devices, \(D_i\) (where \(i\in \{\Alfred, \Beth, \Cathy, 
  \David\}\)), hereafter called their device swarm.
Our system is composted of two network overlays: one protocol is run between the 
devices in \(D_i\) (the Device Swarm Protocol) to gain knowledge on the 
swarm, and another run between different swarms (the Inter-Swarm Protocol) to 
keep global knowledge.
Finally, our file-sharing protocol uses the local and global 
knowledges to coordinate file sharing between devices in different swarms.

@@

\subsection{File-sharing protocol}
\label{FileSharingProtocol}
